---
title: "Re-Audit Analysis"
author: "Mikey Saugstad"
date: "January 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RPostgreSQL)
library(dplyr)
library(ggplot2)
library(tidyr)

# Run the following in console when you want to generate github flavored markdown as well.
# library(rmarkdown)
# render('R/reaudit_analysis.Rmd', c('html_document', 'github_document'))

FIVE_HUNDRED_FEET <- 152.4 # in meters
ONE_THOUSAND_FEET <- 304.8 # in meters
```

```{r connect, echo=FALSE}
pw <- {'sidewalk'}
drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = "sidewalk",
                 host = "localhost", port = 5432,
                 user = "sidewalk", password = pw)
rm(pw)
# dbExistsTable(con, "audit_task")
```


```{r reading.data, echo=FALSE, include=FALSE}
reg.labels <-
  dbGetQuery(con,
            'SELECT label_id, user_id, label_type_id, audit_task.audit_task_id
            FROM audit_task
            INNER JOIN label
            ON audit_task.audit_task_id = label.audit_task_id
            WHERE label.deleted = FALSE
            AND user_id <> \'97760883-8ef0-4309-9a5e-0c086ef27573\'
            AND completed = TRUE')
anon.labels <-
  dbGetQuery(con,
            'SELECT DISTINCT label_id, ip_address AS user_id, label_type_id, audit_task.audit_task_id
            FROM audit_task
            INNER JOIN label
            ON audit_task.audit_task_id = label.audit_task_id
            INNER JOIN audit_task_environment
            ON audit_task.audit_task_id = audit_task_environment.audit_task_id
            WHERE label.deleted = FALSE
            AND user_id = \'97760883-8ef0-4309-9a5e-0c086ef27573\'
            AND completed = TRUE')
reg.audits <-
  dbGetQuery(con,
             'SELECT audit_task.user_id, role.role, audit_task.audit_task_id,
                    street_edge.street_edge_id, ST_LENGTH(ST_TRANSFORM(geom,26918))
            FROM street_edge
            INNER JOIN audit_task
            ON street_edge.street_edge_id = audit_task.street_edge_id
            INNER JOIN user_role
            ON audit_task.user_id = user_role.user_id
            INNER JOIN role
            ON user_role.role_id = role.role_id
            WHERE street_edge.deleted = FALSE
            AND audit_task.user_id <> \'97760883-8ef0-4309-9a5e-0c086ef27573\'
            AND completed = TRUE')
anon.audits <-
  dbGetQuery(con,
             'SELECT DISTINCT ip_address AS user_id, \'Anonymous\' AS role, audit_task.audit_task_id,
                    street_edge.street_edge_id, ST_LENGTH(ST_TRANSFORM(geom,26918))
            FROM street_edge
            INNER JOIN audit_task
            ON street_edge.street_edge_id = audit_task.street_edge_id
            INNER JOIN audit_task_environment
            ON audit_task.audit_task_id = audit_task_environment.audit_task_id
            WHERE street_edge.deleted = FALSE
            AND user_id = \'97760883-8ef0-4309-9a5e-0c086ef27573\'
            AND completed = TRUE')
total.street.distance <-
  dbGetQuery(con,
             'SELECT SUM(ST_LENGTH(ST_TRANSFORM(geom,26918)))
             FROM street_edge
             WHERE deleted = FALSE')
dbDisconnect(con)
```

```{r transforming.data, echo=FALSE, warning=FALSE}
labels <- bind_rows(reg.labels, anon.labels)
audits <- bind_rows(reg.audits, anon.audits)

label.counts <-
  labels %>%
  # filter(label_type_id != 7) %>%
  mutate(user_id = factor(user_id)) %>%
  group_by(user_id) %>%
  summarize_at(vars(label_id), n_distinct) %>%
  rename(label_count = label_id)

audit.length <-
  audits %>%
  mutate(role = factor(role)) %>%
  mutate(user_id = factor(user_id)) %>%
  group_by(user_id, role) %>%
  distinct(audit_task_id, .keep_all = TRUE) %>%
  summarize_at(vars(st_length), sum) %>%
  rename(distance_audited = st_length)

counts <-
  audit.length %>%
  left_join(label.counts, by = 'user_id') %>%
  replace_na(list(label_count = 0)) %>%
  mutate(labels.per.100m = 100 * label_count / distance_audited)

mikey.freq <- (counts %>% filter(user_id == '9efaca05-53bb-492e-83ab-2b47219ee863'))$labels.per.100m
jon.freq <- (counts %>% filter(user_id == '49787727-e427-4835-a153-9af6a83d1ed1'))$labels.per.100m

dist.after.removal <-
  Vectorize(
    function(labels.per.100m.threshold, labels.threshold) {
      good.users <-
        counts %>%
        filter(labels.per.100m >= labels.per.100m.threshold) %>%
        filter(label_count >= labels.threshold)
      
      new.total.dist <-
        audits %>%
        filter(user_id %in% good.users$user_id) %>%
        distinct(street_edge_id, .keep_all = TRUE) %>%
        summarize_at(vars(st_length), sum)
      new.total.dist[[1]]
    }
  )

users.after.removal <-
  Vectorize(
    function(labels.per.100m.threshold, current.role, dist.thresh) {
      good.users <- counts %>%
        filter(distance_audited > dist.thresh) %>%
        filter(labels.per.100m >= labels.per.100m.threshold)
      if (current.role != 'All') good.users <- good.users %>% filter(role == current.role)
      nrow(good.users)
    }
  )

total.dist <- (
  audits %>%
  distinct(street_edge_id, .keep_all = TRUE) %>%
  summarize_at(vars(st_length), sum)
)[[1]]

total.users <- counts %>% nrow()
total.users.five.hundred.feet <- counts %>% filter(distance_audited > FIVE_HUNDRED_FEET) %>% nrow()
total.users.thousand.feet <- counts %>% filter(distance_audited > ONE_THOUSAND_FEET) %>% nrow()

total.users.df <-
  rbind(
    counts %>% group_by(role) %>% summarize(n = n()) %>% mutate(dist.thresh = 0),
    counts %>% filter(distance_audited > FIVE_HUNDRED_FEET) %>%
      group_by(role) %>% summarize(n = n()) %>%
      mutate(dist.thresh = FIVE_HUNDRED_FEET),
    counts %>% filter(distance_audited > ONE_THOUSAND_FEET) %>%
      group_by(role) %>% summarize(n = n()) %>%
      mutate(dist.thresh = ONE_THOUSAND_FEET)
    ) %>%
  mutate(role = as.character(role)) %>%
  add_row(role = 'All', n = total.users, dist.thresh = 0) %>%
  add_row(role = 'All', n = total.users.five.hundred.feet, dist.thresh = FIVE_HUNDRED_FEET) %>%
  add_row(role = 'All', n = total.users.thousand.feet, dist.thresh = ONE_THOUSAND_FEET) %>%
  mutate(role = as.factor(role))
  
get.total.users <-
  Vectorize(
    function(current.role, thresh) {
      total.users.df %>%
        filter(role == current.role, dist.thresh == thresh) %>%
        select(n) %>% as.integer()
    }
  )

max.thresh <- 10
thresh.step <- 0.05
roles.to.look.at <- c('All', 'Anonymous', 'Turker', 'User')
dists.to.look.at <- c(0, FIVE_HUNDRED_FEET, ONE_THOUSAND_FEET)
thresholds.to.look.at <- seq(0, max.thresh, by = thresh.step)

dist.left <-
  data.frame(threshold = thresholds.to.look.at) %>%
  mutate(dist.left = dist.after.removal(threshold, 0))

users.left <-
  expand.grid(threshold = thresholds.to.look.at,
              role = roles.to.look.at,
              dist.thresh = dists.to.look.at,
              stringsAsFactors = FALSE) %>%
  mutate(users.left = users.after.removal(threshold, role, dist.thresh)) %>%
  mutate(percent.of.users = users.left / (get.total.users(role, dist.thresh))) %>%
  mutate(user.definition = factor(dist.thresh, labels = c('Completed >= 1 audit task',
                                                              'Audited >= 500 feet',
                                                              'Audited >= 1000 feet')))

# total.users
# counts %>% filter(distance_audited > FIVE_HUNDRED_FEET) %>% nrow()
# counts %>% filter(distance_audited > FIVE_HUNDRED_FEET) %>% select(role) %>% summary()
# # users.left
# counts %>% filter(distance_audited > FIVE_HUNDRED_FEET) %>% filter(labels.per.100m < 3.75) %>% nrow()
# counts %>% filter(distance_audited > FIVE_HUNDRED_FEET) %>% filter(labels.per.100m < 3.75) %>% select(role) %>% summary()
```

This graph shows what percentage of DC we would have to re-audit (in terms of distance), given different labels/100 meter thresholds for users. For example at x = 5.0, I looked at what our completion percentage would be if we removed the audits from all users who have a labeling frequency of less than 5 labels per 100 meters. For reference, Mikey's label frequency is 6.5 labels/100m, and Jon's is 10.1 labels/100m. I added lines vertical lines on the graph below for each of us; I also added a line at my recommended cutoff of 3.75 labels/100m.

```{r plotting, echo=FALSE}
ggplot(data = dist.left, aes(x = threshold, y = 100 - (100 * dist.left / total.dist))) +
  geom_line() +
  geom_vline(xintercept = mikey.freq) +
  geom_vline(xintercept = 3.75) +
  xlab('Labels per 100 Meters Threshold') +
  ylab('Percentage to Re-Audit (distance)') +
  theme_bw()

ggplot(data = users.left %>% filter(role == 'All'),
       aes(x = threshold, y = 100 - (100 * percent.of.users))) +
  geom_line(aes(colour = user.definition)) +
  geom_vline(xintercept = mikey.freq) +
  geom_vline(xintercept = 3.75) +
  xlab('Labels per 100 Meters Threshold') +
  ylab('Percentage of Users Removed') +
  theme_bw()
ggplot(data = users.left %>% filter(dist.thresh == 0),
       aes(x = threshold, y = 100 - (100 * percent.of.users))) +
  geom_line(aes(colour = role)) +
  geom_vline(xintercept = mikey.freq) +
  geom_vline(xintercept = 3.75) +
  xlab('Labels per 100 Meters Threshold') +
  ylab('Percentage of Users Removed') +
  ggtitle('Users Who Completed >= 1 Audit Task') +
  theme_bw()
ggplot(data = users.left %>% filter(dist.thresh == FIVE_HUNDRED_FEET),
       aes(x = threshold, y = 100 - (100 * percent.of.users))) +
  geom_line(aes(colour = role)) +
  geom_vline(xintercept = mikey.freq) +
  geom_vline(xintercept = 3.75) +
  xlab('Labels per 100 Meters Threshold') +
  ylab('Percentage of Users Removed') +
  ggtitle('Users Who Audited >= 500ft') +
  theme_bw()
ggplot(data = users.left %>% filter(dist.thresh == ONE_THOUSAND_FEET),
       aes(x = threshold, y = 100 - (100 * percent.of.users))) +
  geom_line(aes(colour = role)) +
  geom_vline(xintercept = mikey.freq) +
  geom_vline(xintercept = 3.75) +
  xlab('Labels per 100 Meters Threshold') +
  ylab('Percentage of Users Removed') +
  ggtitle('Users Who Audited >= 1000ft') +
  theme_bw()
```

And here are some summary statistics for the users:

```{r user.summary.stats, echo=FALSE}
summary(counts %>%
          select(-user_id))
```

